Constructing the transition graphs of interacting hysterons

### 2022-06-24 Paper_draft.tex
Reworked base graph method overview using Tikz

\usepackage[pdftex]{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[table]{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

    \includegraphics[width=0.5\textwidth]{breakdown_sketch.png}

>>>>

\usepackage[pdftex]{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[table]{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{decorations.pathreplacing,calligraphy}
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\begin{tikzpicture}[squarednode/.style={rectangle, draw=black, fill=white, thick, minimum size=3mm}]
\node[squarednode](mainloop){Main loop};
\node[squarednode](scrambling)[right=of mainloop] {Scrambling};
\node[squarednode](avalanches)[right=of scrambling] {Avalanches};
\node[squarednode](finalgraph)[right=of avalanches] {Final graph};

\draw[->, very thick] (mainloop.east) -- (scrambling.west);
\draw[->, very thick] (scrambling.east) -- (avalanches.west);
\draw[->, very thick] (avalanches.north) arc (-80:260:10pt)
node[pos=0.5, above=2pt]{Iterate over $l$};
\draw[decorate, decoration = {calligraphic brace, amplitude=6pt,raise=10pt}, very thick] (mainloop.west)  -- (scrambling.east)
node[pos=0.5,above=15pt,black] {Base graph};
\draw[decorate, decoration = {calligraphic brace, amplitude=6pt,raise=10pt}, very thick] (avalanches.east)  -- (scrambling.west)
node[pos=0.5, below=15pt,black] {Only with coupling}; 
\draw[->, very thick] (avalanches.east) -- (finalgraph.west);
\end{tikzpicture}
